ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-17 pathways_to_impact.tex
Neil initial attempt

>>>>

See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.

We will work with researchers at the College of Policing, the Behavioural Insights Team at West Midlands Police,

Our day-to-day contact at West Midlands Police is Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning). Our day-to-day contact at the West Midlands Police and Crime Commissioner's Office is Alison Spence.

At the level of the National Police Chiefs' Council we will work with Deputy Chief Constable Louisa Rolfe who is the lead for domestic abuse.

In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry. The summit will be a 50/50 academic / practitioner mix. We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior managment team: 1. The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse. 2. The programme on the  ``decision to report'' can link with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting. 3. The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands,

At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015. (https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse. (https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf) We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.

Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability. Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders. Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship. Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team. We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.

Events:

Impact summit (1 day at the Shard)
Visits to key charities
Visits to West Midlands Police
Presentation to NPCC
Data sprint session with WMP Behavioural Insights Team?

In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts. We will submit these reports to the College of Police What Works database and log them on the Research Map (https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx)

Although a high-profile ``launch'' event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme, and this is also an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts. Trendl will spend one third of her time on the programme on the impact activities.

We will apply to the Warwick ESRC Impact Acceleration Fund and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.
